Challenges and Solutions of Developing and Implementing a Revolutionary Novel Desktop-as-a-Service

### 2024-04-26 paper.tex
More content (e.g. Abstract)

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
%
\usepackage[T1]{fontenc}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
%\usepackage{color}
%\renewcommand\UrlFont{\color{blue}\rmfamily}
%\urlstyle{rm}
%
\begin{document}
%
\title{Challenges and Solutions of Developing and
	Implementing a Revolutionary Novel Desktop-as-a-Service}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Christian Baun \and 
Johannes Bouché}
% \author{Christian Baun\orcidID{0009-0004-9955-3752} \and
% 	Johannes Bouché\orcidID{TODO}}
%
\authorrunning{C. Baun, J. Bouché}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Faculty of Computer Science and Engineering,\\
Frankfurt University of Applied Sciences,\\
Nibelungenplatz 1, 60318 Frankfurt am Main, Germany
\email{[christianbaun|johannes.bouche]@fb2.fra-uas.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
	The paper will cover very novel and non-published knowledge we gained
	from developing and implementing a DaaS that is funded by the German
	Federal Ministry for Economic Affairs and Climate Action. The topic
	fits very well into the topics of the conference. TODO: Christian

@@

This paper discusses challenges during the development and implementation of a novel Desktop-as-a-Service (DaaS) solution that enables the deployment and usage of unmodified Linux and Windows applications in the same way as web applications and can run inside public resources but can also be deployed in a private context. Since all interaction with the DaaS and the applications that reside inside is done via a user's web browser, the users can use any client, no matter what hardware or host operating system it is compromised of. A browser is the only software component required to use the novel DaaS service DESIGN.

@@

Celesti et al.~\cite{celesti2016improving} implemented in 2016 a DaaS using OpenStack and analyzed the characteristics and performance aspects of using noVNC, SPICE, and Apache Guacamole as solutions for providing access to the desktop via a browser. One focus of the paper is the redirection of the sound interface of the virtual desktop. The paper's authors conclude that Guacamole, in combination with the protocol RDP, is the best solution. The authors evaluated the lag time for remote audio playback in an Internet scenario. by measuring the time between the automated initiation of the live streaming using the VLC media player software and the arrival of the music data by analyzing network traffic via monitoring software Wireshark. When using Guacamole combined with the protocol RDP, the average lag was around 750\,ms. When using Guacamole combined with the protocol VNC, the average lag was around 1750\,ms. The paper also includes a short evaluation of the lag for video frames represented by background color changes of a Java application. Again, the configuration Guacamole and RDP offered the best performance video update with an average lag of around 300\,ms. The configuration of Guacamole and VNC caused an average lag of around 500\,ms.

Magana et al.~\cite{magana2019remote} compared in 2019 the most popular remote desktop protocols and software implementations. The authors analyzed five protocols: PCoIP used in the Amazon WorkSpaces, Microsoft RDP, TeamViewer, VNC, and Citrix Independent Computing Architecture (ICA). In the paper, the network transfer rate and its relation to the quality experienced by the DaaS user are evaluated by assuming three scenarios: using an office software suite, web browsing, and video streaming. One emphasis of the paper is comparing the transfer rate of the different protocols for three scenarios. In the Office Software Suite scenario, the transfer rate is measured and compared when performing several different tasks like opening and editing a document (typing), loading an image, and saving a document. The web browsing scenario covers requesting three different web pages, and for the video streaming scenario, the same YouTube video file was viewed at different resolutions. The authors conclude that RDP requires fewer downstream and upstream network resources for all three scenarios. It is important to understand that the protocols RDP and VNC are implemented in open-source projects and proprietary solutions for many different operating systems. Depending on the different quality levels of the many existing implementations, it is difficult to generalize about the performance of the protocols, as individual implementations may have better or worse performance characteristics than expected.

@@

Developing the automatic adaptation of the output to the limits of the respective application window is challenging. Only a few RDP and VNC server implementations offer to export the graphical output of only individual windows or processes. For Windows operating systems, the proprietary built-in RDP server and the free software TightVNC offer the export of full desktops and single windows. For Linux operating system deployments, the free software projects xrdp and x11vnc enable all desired features. Table ~\ref{tab:DaaS_Services_Overview} includes an overview of the mentioned service implementations for RDP and VNC protocols and their relevant characteristics. Further implementations like TigerVNC and protocols like NoMachine NX exist but do not seem useful in a novem DaaS design and implementation because they do not meet all feature requirements.~\cite{OJCC_2023v8i1n01_Baun}

@@

The automatic adaptation of browser tabs content size, is done by.... TOTO: Johannes...

>>>>

% This is samplepaper.tex, a sample chapter demonstrating the
% LLNCS macro package for Springer Computer Science proceedings;
% Version 2.21 of 2022/01/12
%
\documentclass[runningheads]{llncs}
%
\usepackage[T1]{fontenc}
% T1 fonts will be used to generate the final print and online PDFs,
% so please use T1 fonts in your manuscript whenever possible.
% Other font encondings may result in incorrect characters.
%
\usepackage{graphicx}
% Used for displaying a sample figure. If possible, figure files should
% be included in EPS format.
%
% If you use the hyperref package, please uncomment the following two lines
% to display URLs in blue roman font according to Springer's eBook style:
%\usepackage{color}
%\renewcommand\UrlFont{\color{blue}\rmfamily}
%\urlstyle{rm}
%
\begin{document}
%
\title{Challenges and Solutions of Developing and
	Implementing a Revolutionary Novel Desktop-as-a-Service}
%
%\titlerunning{Abbreviated paper title}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Christian Baun \and 
Johannes Bouché}
% \author{Christian Baun\orcidID{0009-0004-9955-3752} \and
% 	Johannes Bouché\orcidID{TODO}}
%
\authorrunning{C. Baun, J. Bouché}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Faculty of Computer Science and Engineering,\\
Frankfurt University of Applied Sciences,\\
Nibelungenplatz 1, 60318 Frankfurt am Main, Germany
\email{[christianbaun|johannes.bouche]@fb2.fra-uas.de}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
Desktop-as-a-Service (DaaS) is a cloud service category with great potential for improving the everyday work of running and using applications. However, existing DaaS solutions have several drawbacks, which have limited the popularity of this service category in the past. Our novel DaaS solution not only overcomes the limitations of existing solutions but also offers significant benefits. It has the potential to revolutionize the way we use applications, supporting non-modified Linux and Windows applications with just a browser on the client side. This paper describes some of the knowledge we gained during the development because of the challenges we faced and the solutions we found.

@@

This paper discusses challenges during the development and implementation of a novel Desktop-as-a-Service (DaaS) solution that enables the deployment and usage of unmodified Linux and Windows applications in the same way as web applications and can run inside public resources but can also be deployed in a private context. Since all interaction with the DaaS and the applications that reside inside is done via a user's web browser, the users can use any client, no matter what hardware or host operating system it is compromised of. A browser is the only software component required to use the novel DaaS service.

@@

Celesti et al.~\cite{celesti2016improving} implemented in 2016 a DaaS using OpenStack~\cite{sefraoui2012openstack} and analyzed the characteristics and performance aspects of using noVNC, SPICE, and Apache Guacamole as solutions for providing access to the desktop via a browser. One focus of the paper is the redirection of the sound interface of the virtual desktop. The paper's authors conclude that Guacamole, in combination with the Remote Desktop Protocol (RDP), is the best solution. The authors evaluated the lag time for remote audio playback in an Internet scenario. by measuring the time between the automated initiation of the live streaming using the media player software VLC and the arrival of the music data by analyzing network traffic via monitoring software Wireshark. When using Guacamole combined with the protocol RDP, the average lag was around 750\,ms. When using Guacamole combined with the protocol Virtual Network Computing (VNC), the average lag was around 1750\,ms. The paper also includes a short evaluation of the lag for video frames represented by background color changes of a Java application. Again, the configuration Guacamole and RDP offered the best performance video update with an average lag of around 300\,ms. The configuration of Guacamole and VNC caused an average lag of around 500\,ms.

Magana et al.~\cite{magana2019remote} compared in 2019 the most popular remote desktop protocols and software implementations. The authors analyzed five protocols: PCoIP used in the Amazon WorkSpaces, RDP, TeamViewer, VNC~\cite{rfc6143}, and Citrix Independent Computing Architecture (ICA). In the paper, the network transfer rate and its relation to the quality experienced by the DaaS user are evaluated by assuming three scenarios: using an office software suite, web browsing, and video streaming. One emphasis of the paper is comparing the transfer rate of the different protocols for three scenarios. In the Office Software Suite scenario, the transfer rate is measured and compared when performing several different tasks like opening and editing a document (typing), loading an image, and saving a document. The web browsing scenario covers requesting three different web pages, and for the video streaming scenario, the same YouTube video file was viewed at different resolutions. The authors conclude that RDP requires fewer downstream and upstream network resources for all three scenarios. It is important to understand that the protocols RDP and VNC are implemented in open-source projects and proprietary solutions for many different operating systems. Depending on the different quality levels of the many existing implementations, it is difficult to generalize about the performance of the protocols, as individual implementations may have better or worse performance characteristics than expected.

@@

Developing the automatic adaptation of the output to the limits of the respective application window is challenging. Only a few RDP and VNC server implementations offer to export the graphical output of only individual windows or processes. For Windows operating systems, the proprietary built-in RDP server and the free software TightVNC offer the export of full desktops and single windows. For Linux operating system deployments, the free software projects xrdp and x11vnc enable all desired features. Table ~\ref{tab:DaaS_Services_Overview} includes an overview of the mentioned service implementations for RDP and VNC protocols and their relevant characteristics. Further implementations like TigerVNC and protocols like NX NoMachine exist but do not seem useful for designing and implementing a novel DaaS because they do not meet all feature requirements.~\cite{OJCC_2023v8i1n01_Baun}

@@

The automatic adaptation of browser tabs content size, is done by.... TOTO: Johannes´...
